### 2023-08-23 appendix.tex
section

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial vector $\textbf{u}$ and initial state $q_0$.
To do so, we construct a reset-VASS $V_2$
with initial vector $\textbf{v}$ and initial state $q'_0$
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

@@

The initial vector $\textbf{v}$ is constructed from $\textbf{u}$ by having at least $1$ on the first two additional vector coordinate.

@@

% Note that all transitions of $T_1$ are in conflict and, by construction if not by definition, no more than one transition can fire at a time.

These first two additional vector coordinate together with this additional transition allow
to reach any reachable vector and control-state $q$ and then to freeze the configuration.

@@

Now we need to see if that vector is zero.
% Now we need to see if that marking is zero.

We introduce two new additional vector coordinate and $d$ new transitions which have
$-1$ on the $d$-th vector coordinate and $+1$ on this penultimate coordinate.

@@

Now if $q(\textbf{0})$ is reachable from $q_0(\textbf{u})$ in $V_1$, then $V_2$ can also reach a similar
vector $q(0,0,0,\ldots, 0, 1,0,0,0)$ by executing the same sequence of transition.
Then $s$ can freeze the $V_1$ subset,
% Now if $0$ is reachable in $R(C_1, \mu_1)$  then the net $C_2$ can also reach this marking in the place of $P_1$ by executing the same sequence of transition firings. Then $s$ can fire, freezing the $C_1$ subset.
ending up in $q(0^{d+4})$, and $V_2$ is not live.
% Since $mu(p_i) = 0$ for all $p_i \in P_1$, no transition $s_{p_i}$ with $p_i \in P_1$ can fire, and $C_2$ is dead.
Thus if $q(\textbf{0})$ is reachable then $V_2$ is not live.

>>>>

We wish to determine if $q(\textbf{0})$ is reachable in a reset-VASS $V_1$
with
initial vector $\textbf{u}$ and initial \alain{control-}state $q_0$.\alain{incohérent: control-state !, notation $q_0(\textbf{u})$  à utiliser}
To do so, we construct a reset-VASS $V_2$
with initial vector $\textbf{v}$ and initial state $q'_0$ \alain{idem}
which is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

@@

The initial vector $\textbf{v}$ is constructed from $\textbf{u}$ by having at least $1$ on the first two additional vector coordinate.
\alain{un dessin aiderait...}

@@

% Note that all transitions of $T_1$ are in conflict and, by construction if not by definition, no more than one transition can fire at a time.
\alain{donne des noms, numéros,...}
These first two additional vector coordinate together with this additional transition allow
to reach any reachable vector and control-state $q$ and then to freeze the configuration.

@@

Now we need to see if that vector is zero.
% Now we need to see if that marking is zero.
\alain{structurer la preuve pour la rendre lisible, nommer les objets, faire des paragraphes,...}
We introduce two new additional vector coordinate and $d$ new transitions which have
$-1$ on the $d$-th vector coordinate and $+1$ on this penultimate coordinate.

@@

Now if $q(\textbf{0})$ is reachable from $q_0(\textbf{u})$ in $V_1$, then $V_2$ can also reach a similar
vector $q(0,0,0,\ldots, 0, 1,0,0,0)$ by executing the same sequence of transitions.
Then $s$ can freeze the $V_1$ subset,
% Now if $0$ is reachable in $R(C_1, \mu_1)$  then the net $C_2$ can also reach this marking in the place of $P_1$ by executing the same sequence of transition firings. Then $s$ can fire, freezing the $C_1$ subset.
ending up in $q(0^{d+4})$, and $V_2$ is not live.
% Since $mu(p_i) = 0$ for all $p_i \in P_1$, no transition $s_{p_i}$ with $p_i \in P_1$ can fire, and $C_2$ is dead.
Thus if $q(\textbf{0})$ is reachable then $V_2$ is not live.
